Discrete Quantum Theories and Computing

### 2018-03-17 dissertation.tex
dissertation.lyx Before install LyX 2.3.0

\todo{Further explain $\sigma_{\mu}^{j}$ used as a quantum circuit,
control not, the Deutsch quantum black box~\cite{NCbook}, and maybe
Deutsch Algorithm...}

@@

Our next objective is to develop more realistic discrete quantum theory
variants that exclude ``supernatural'' algorithms such as the one
presented above. Our first such plausible framework~\cite{powerdqc}
is based on complexifiable finite fields. To incorporate complex numbers
for quantum amplitudes, we exploit the fact that the polynomial $x^{2}+1=0$
is \emph{irreducible} (has no solution) over a prime field $\ff{p}$
with $p$ odd if and only if $p$ is of the form~$4\ell+3$, with
$\ell$ a non-negative integer. In other words, $x^{2}+1=0$ is irreducible
over $\ff{3},\ff{7},\ff{11},\ff{19},\ldots$. We achieve our goal
by observing that any field in this family is extensible to a field~$\ff{p^{2}}$
whose elements can be viewed as discrete complex numbers with the
real and imaginary parts in~$\ff{p}$. In the field~$\ff{p^{2}}$,
the Frobenius automorphism of an element $\alpha$ (defined as $\alpha^{p}$)
represents the usual definition of complex conjugation~\cite{fieldexample}.

>>>>

\todo{Further explain $\sigma_{\mu}^{j}$ used as a quantum circuit,
control not, the Deutsch quantum black box~\cite{544199}, and maybe
Deutsch Algorithm...}

@@

Our next objective is to develop more realistic discrete quantum theory
variants that exclude ``supernatural'' algorithms such as the one
presented above. Our first such plausible framework~\cite{HOSW2011}
is based on complexifiable finite fields. To incorporate complex numbers
for quantum amplitudes, we exploit the fact that the polynomial $x^{2}+1=0$
is \emph{irreducible} (has no solution) over a prime field $\ff{p}$
with $p$ odd if and only if $p$ is of the form~$4\ell+3$, with
$\ell$ a non-negative integer. In other words, $x^{2}+1=0$ is irreducible
over $\ff{3},\ff{7},\ff{11},\ff{19},\ldots$. We achieve our goal
by observing that any field in this family is extensible to a field~$\ff{p^{2}}$
whose elements can be viewed as discrete complex numbers with the
real and imaginary parts in~$\ff{p}$. In the field~$\ff{p^{2}}$,
the Frobenius automorphism of an element $\alpha$ (defined as $\alpha^{p}$)
represents the usual definition of complex conjugation~\cite{fieldexample}.
